---
title: "Hw2 Bolin Wang"
author: "Bolin Wang"
date: "2020/9/2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 1.import data from github
```{r}
Hw1<- read.csv("https://github.com/kijohnson/ADA-FAll-2020/raw/master/Class%20One/Class%201%20Survey%20Fall%202020.csv")
```

# 2.number of observation(32) and variables(27)

```{r}
dim(Hw1)
```

# 3a.rename column names

```{r}
names(Hw1)[2:27]<-c("like_cat","like_dog","iitem","slogan","day_of_week","time","fFood","fDrink","fMonth","hobby","program","speciallization","Ssofware","Rexp","Cconfort","level","Cexp","LinC","PHintres","Fnumber","bday","bmonth","country","state","city","edulevel")

```

# 4.count the number of different virable type
```{r}
table(sapply(Hw1, class))
```

# 5a. find unusual variable
```{r}
Hw1$bday%in%(1:31)
Hw1$bmonth%in%(1:12)
```

# 5b.replace word to number and calculate median
```{r}
library(plyr)
Hw1[which(Hw1$bday=='26-Mar')]$bday<-"26"
median(subset(Hw1$bday,Hw1$bday%in%(1:31)))

Hw1$bmonth<-as.numeric(Hw1$bmonth)

Hw1[which(Hw1$bmonth=='december')]$bmonth<-"12"
Hw1[which(Hw1$bmonth=='August')]$bmonth<-"8"
median(subset(Hw1$bmonth,Hw1$bmonth%in%(1:12)))
```
# 6a new bseason variable
```{r}
Hw1$bseason[Hw1$bmonth%in%c(1,2,12)]<-"winter"
Hw1$bseason[Hw1$bmonth%in%c(3,4,5)]<-"spring"
Hw1$bseason[Hw1$bmonth%in%c(6,7,8)]<-"summer"
Hw1$bseason[Hw1$bmonth%in%c(9,10,11)]<-"fall"
```

# 6b season,bmonth table
```{r}
table(Hw1$bmonth,Hw1$bseason)
```

#6c addmargins to count sum of bseason. 
# spring=8, summer=7, fall=8, winter=7)
```{r}
addmargins(table(Hw1$bmonth,Hw1$bseason)) 
```
# 7 How many students are in dfferent education level? 
```{r}
library(plyr)
count(Hw1$edulevel)
```
## sum the numer of students' education degree by using count function#

